%% Tanmoy Sanyal — Curriculum Vitae
%% Compile with: pdflatex tsanyal_resume.tex
%% Requires: lmodern, geometry, enumitem, titlesec, hyperref, microtype, xcolor, parskip

\documentclass[10pt, letterpaper]{article}

% ── Packages ──────────────────────────────────────────────────────────────────
\usepackage[T1]{fontenc}
\usepackage{lmodern}
\usepackage{microtype}
\usepackage[
  top=0.8in,
  bottom=0.8in,
  left=0.9in,
  right=0.9in
]{geometry}
\usepackage{titlesec}
\usepackage{enumitem}
\usepackage{parskip}
\usepackage{xcolor}
\usepackage{hyperref}
\usepackage{array}

% ── Palette & typography ─────────────────────────────────────────────────────
\definecolor{accent}{HTML}{1F3A5F}
\definecolor{muted}{HTML}{4A5568}
\definecolor{rulegray}{HTML}{C5CCD6}

\hypersetup{
  colorlinks=true,
  linkcolor=accent,
  urlcolor=accent,
  pdftitle={Tanmoy Sanyal -- CV},
  pdfauthor={Tanmoy Sanyal}
}

\pagestyle{empty}
\setlength{\parskip}{0pt}
\setlength{\parindent}{0pt}

% ── Section headings ─────────────────────────────────────────────────────────
\titleformat{\section}
  {\color{accent}\normalfont\large\bfseries\scshape}
  {}{0em}{}
  [\vspace{2pt}{\color{rulegray}\titlerule[0.5pt]}\vspace{5pt}]
\titlespacing{\section}{0pt}{11pt}{4pt}

% ── Lists ────────────────────────────────────────────────────────────────────
\setlist[itemize]{
  leftmargin=1.35em,
  itemsep=2.5pt,
  topsep=3pt,
  parsep=0pt,
  partopsep=0pt,
  label={\color{accent}\textbullet}
}

% ── Helpers ──────────────────────────────────────────────────────────────────
\newcommand{\employer}[1]{\textbf{\color{accent}#1}}
\newcommand{\jobtitle}[1]{\textit{#1}}
\newcommand{\daterange}[1]{\textit{\color{muted}#1}}
\newcommand{\contactsep}{\enspace\textcolor{rulegray}{\textbullet}\enspace}

\newcommand{\jobheader}[3]{%
  \employer{#1} --- \textcolor{muted}{#2} \\[2pt]
  #3\par
}

\newcommand{\roletime}[2]{%
  \jobtitle{#1} \hfill \daterange{#2}\par\vspace{1pt}
}

% ─────────────────────────────────────────────────────────────────────────────
\begin{document}

%% ── HEADER ──────────────────────────────────────────────────────────────────
{\fontsize{20}{24}\selectfont\color{accent}\textbf{Tanmoy Sanyal}}

\vspace{4pt}
{\large\textit{Scientist, Protein Design \& Structural Biology}}

\vspace{5pt}
{\color{muted}San Francisco Bay Area, CA}

\vspace{6pt}
{\small
  \href{mailto:tanmoy.7989@gmail.com}{tanmoy.7989@gmail.com}\contactsep
  (805) 637-0375\contactsep
  \href{https://tanmoy7989.github.io}{tanmoy7989.github.io}\contactsep
  \href{https://linkedin.com/in/tanmoy-sanyal}{LinkedIn}\contactsep
  \href{https://github.com/tanmoy7989}{GitHub}
}

\vspace{10pt}
{\color{muted}\linespread{1.08}\selectfont
Computational scientist with over a decade of experience developing physics-based and
machine learning methods for protein design and structural biology, with a track record
spanning academic research, biotech, and large pharma. Specialized in MLOps, multispecific
molecule design, and integrative structural modeling. Demonstrated ability to translate
rigorous scientific methods into scalable, cloud-native production systems.
\par}

%% ── EDUCATION ───────────────────────────────────────────────────────────────
\section{Education}

\textbf{University of California, Santa Barbara} \\
\jobtitle{Ph.D., Chemical Engineering} --- Graduate Emphasis in Computational Science \& Engineering (HPC) \hfill \daterange{2013--2018}

\vspace{5pt}
\textbf{Indian Institute of Technology, Kharagpur} \\
\jobtitle{Integrated M.Tech \& B.Tech (Hons.), Chemical Engineering} \hfill \daterange{2008--2013}

%% ── EXPERIENCE ──────────────────────────────────────────────────────────────
\section{Experience}

\jobheader{Amgen Inc.}{South San Francisco, CA}{%
  \roletime{Principal Protein Design Scientist}{Apr 2024--Present}
  \roletime{Senior Protein Design Scientist}{Oct 2023--Mar 2024}
  \roletime{Protein Design Scientist}{Jan 2022--Oct 2023}
}
\begin{itemize}
  \item \textbf{Multispecifics design platform:} Developed cloud-native, highly parallelized
    ODE solvers for pharmacokinetic modeling of bispecific molecules; deployed via ML
    regression models achieving a \textbf{50$\times$ speedup}.

  \item \textbf{Statistical mechanics of multispecifics:} Translated statistical mechanical
    models of superselectivity (originally developed for multivalent ligands) to multispecific
    molecules; currently undergoing experimental validation and benchmarking on bispecific
    candidates.

  \item \textbf{MLOps architecture:} Built Amgen's first end-to-end, cloud-native MLOps
    pipeline for supervised biophysical property prediction from protein sequences, now used
    across \textbf{8+ antibody design projects}. Mentored junior data scientists in
    thermostability prediction workflows.

  \item \textbf{In-silico display library design:} Developed linear-programming algorithms to
    optimize degenerate codon libraries using protein language models. Set an internal record
    for fastest request-to-delivery (${\sim}$3~days) for a 1M+ diverse antibody library;
    applied to engineer cross-reactivity across 2 therapeutic areas.

  \item \textbf{Biologics design:} Designed mini-binders for a rare disease target using
    Rosetta-ddG and the AlphaFold, RFDiffusion, and ProteinMPNN workflow. Developed an
    active-learning pipeline (Gaussian process regression) yielding a
    \textbf{20$\times$} affinity improvement over 3 design-and-screen iterations.

  \item \textbf{AlphaFold cloud deployment:} Collaborated with AWS to re-tool open-source
    AlphaFold-2 into a scalable cloud-native version supporting ${\sim}$100k sequences; now
    in regular use for variant design.
\end{itemize}

\vspace{5pt}
\jobheader{Novo Nordisk Research Center Seattle}{Seattle, WA}{%
  \roletime{Protein Design Scientist}{2022--2023}
}
\begin{itemize}
  \item \textbf{Peptide modifications for half-life extension:} Developed a computational
    method for systematically scanning PEGylation sites on peptides for half-life
    protraction. Published and open-sourced the method with a benchmark on GLP-1 analogs
    relevant to anti-obesity therapeutics.
\end{itemize}

\vspace{5pt}
\jobheader{University of California, San Francisco}{Sali Lab}{%
  \roletime{Postdoctoral Scholar}{Jan 2019--Jan 2022}
}
\begin{itemize}
  \item \textbf{Nanobody biophysics \& vaccine design:} Developed a protein--protein docking
    score for nanobody interactions with the SARS-CoV-2 Spike protein using chemical
    crosslinking and escape mutation data; identified vulnerable and resilient epitopes across
    variants of concern. Also performed MD simulation studies elucidating the effects of
    framework mutations on distal CDR3 residues.

  \item \textbf{Protein structure modeling from crosslinks:} Developed graph-sampling
    algorithms to extract domain boundaries from chemical crosslinking data; published the
    first coarse-grained structure of the full SMC5/6 protein complex.

  \item \textbf{Whole-cell digital twin:} Developed Bayesian networks combining
    pharmacokinetic, Brownian dynamics, and enzyme-pathway models of the pancreatic
    beta-cell into a proof-of-concept multimodal digital twin. Served as software lead in
    the Pancreatic Beta-Cell Consortium (UCSF/USC).
\end{itemize}

\vspace{5pt}
\jobheader{University of California, Santa Barbara}{Shell Lab}{%
  \roletime{Ph.D.\ Researcher}{2013--2018}
}
\begin{itemize}
  \item \textbf{Coarse-graining for phase separation:} Introduced the local density potential
    for structurally and thermodynamically accurate coarse-grained MD simulations of
    liquid--liquid phase separation.

  \item \textbf{Protein folding via variational inference:} Developed backbone models for
    template-free folding of 200+ residue protein domains using MD simulations, and for
    studying self-assembly in amyloidogenic peptides.

  \item \textbf{HPC cluster administration:} Set up and administered a 144-core Linux
    (Rocks~6.2) cluster; wrote utilities for automated resource sharing among lab members.
\end{itemize}

%% ── COMPUTATIONAL SKILLS ────────────────────────────────────────────────────
\section{Computational Skills}

\begin{tabular}{@{}>{\bfseries\color{accent}}l@{\hspace{0.75em}}>{\raggedright\arraybackslash}p{\dimexpr\linewidth-1.55in-2\tabcolsep}@{}}
  Protein Design      & Rosetta, RFDiffusion, ProteinMPNN, AlphaFold, ESM2, Amplify (protein language models) \\
  Molecular Modeling  & OpenMM, LAMMPS, GROMACS, IMP, Modeller, UCSF ChimeraX, PyMOL \\
  ML / MLOps          & PyTorch, PyTorch-Lightning, TensorFlow-Probability, PyMC3, MLFlow, AWS Batch \\
  Languages           & Python (+Cython, 10k+ lines), C++ (${\sim}$4k lines), Fortran-90 (${\sim}$1k lines), Bash \\
\end{tabular}

%% ── OPEN-SOURCE SOFTWARE ────────────────────────────────────────────────────
\section{Open-Source Software}

\begin{itemize}
  \item \textbf{nnprotscan} --- Computational scanning of chemical modifications in peptides.
  \item \textbf{nbspike} --- Integrative epitope prediction for nanobody--antigen interactions.
  \item \textbf{IMP-raindrops} --- Crosslink-guided domain discovery within the IMP framework.
  \item \textbf{PDB-Dev deposition tools} --- Structural deposition utilities for the SMC5/6 complex.
  \item \textbf{LAMMPS local density potential} --- Plugin implementing the local density coarse-graining potential.
\end{itemize}

%% ── SELECTED PUBLICATIONS ──────────────────────────────────────────────────
\section{Selected Publications}

{\small
\begin{itemize}[itemsep=3pt, topsep=2pt]
  \item N.~Thomas, \textbf{T.~Sanyal}, P.~Greisen~Jr.\ \& K.~Diebler.
    Structure-Based Computational Scanning of Chemical Modification Sites in Biologics.
    \textit{ACS Omega}, 9(34), 36787--36794, 2024.

  \item F.D.~Mast, P.C.~Fridy, N.E.~Karen, J.~Wang, E.Y.~Jacobs, J.P.~Olivier,
    \textbf{T.~Sanyal}, et al.\ Highly synergistic combinations of nanobodies that target
    SARS-CoV-2 and are resistant to escape. \textit{eLife}, 10: e73027, 2021.

  \item B.~Raveh, L.~Sun, K.L.~White, \textbf{T.~Sanyal}, et al.\
    Bayesian metamodeling of complex biological systems across varying representations.
    \textit{PNAS}, 118(35) e2104559118, 2021.

  \item Y.~Yu, S.~Li, Z.~Ser, \textbf{T.~Sanyal}, et al.\
    Integrative analysis reveals unique structural and functional features of the Smc5/6
    complex. \textit{PNAS}, 118(19) e2026844118, 2021.

  \item \textbf{T.~Sanyal}, J.~Mittal and M.~Scott~Shell.
    A hybrid, bottom-up, structurally-accurate, Go-like coarse-grained protein model.
    \textit{J.\ Chem.\ Phys.}, 151(4): 044111, 2019.

  \item \textbf{T.~Sanyal} and M.~Scott~Shell.
    Coarse-grained models using local-density potentials optimized with the relative
    entropy: Application to implicit solvation.
    \textit{J.\ Chem.\ Phys.}, 145, 034109, 2016.
\end{itemize}
}

%% ── SERVICE & PEER REVIEW ──────────────────────────────────────────────────
\section{Service \& Peer Review}

\textit{Reviewer} (2019--Present): \textit{Structure}; \textit{Journal of Physical
Chemistry}; \textit{Proteins: Structure, Function and Bioinformatics};
\textit{Review of Scientific Instruments}; \textit{Rapid Reviews COVID-19}; \textit{Life}.

\end{document}
